Whats reported in the news?

### 2018-03-13 paper/docs/04_Modelresults_50.Rmd
change topic names

```{r}
topics <- matrix(c(1, "SPD", 2, "B90/ Die Grüne & DIE LINKE", 3, "Mix: Akhanli, Guttenberg, Bayern", 4, "Great Coalition debates", 5, "Diesel scandal", 6, "H.Kohl", 7, "Federal Election results", 8, "Europa, Macron, Schäuble", 9, "Mix: political trends, twitter", 10, "Merkel vs. Schulz", 11, "politics & democracy in GER", 12, "Deportation of criminal Refugees", 13, "A.Merkel", 14, "Text processing fail", 15, "Israel, antisemitism, D.Trump", 16, "Mix: political talkshows, Refugees", 17, "Votes within SPD", 18, "Election in Niedersachsen", 19, "R.Lammert", 20, "AfD, Right-wing extremist tendencies", 21, "German armed forces, v.d.Leyen", 22, "SPD, stuffing debates", 23, "CSU, Söder vs. Seehover, refugee cap", 24, "Bundespräsident F.-W.Steinmeier", 25, "Election polls", 26, "Jamaica failure", 27, "Jamaica Coalition debates", 28, "G20 in Hamburg", 29, "Federal Constitutional Court, Ministry of the Interior", 30, "F.Petri, AfD", 31, "D.Trump, Russia", 32, "Gauland, Weidel, AfD", 33, "German armed forces, Mali", 34, "Mix: Children, Education, Women", 35, "Left- rightwing Terror, police reports", 36, "Mix: people, Germany, democracy", 37, "AfD in parliament", 38, "EU policies", 39, "Mix: Terror attacks", 40, "Mix: Metoo, SPD", 41, "Terror attack Berlin (Amri)", 42, "Refugee family reunion", 43, "Mix: studies", 44, "Federal Constitutional Court (NSU, Franco, Terror)", 45, "Mix: minister of the interior, environment", 46, "CDU, J.Spahn, Tauber (Disease)", 47, "Church", 48, "public (budget) statistics, Education/ Healthcare/ Digital policies", 49, "Turkey", 50, "Höcke, Holocaust"), ncol=2, byrow=T)

@@

```{r eval=FALSE, include=FALSE}
# Inspect the unclear topics
btw.2 %>% filter(topic==13) %>% select(title, gamma, url) %>%
  arrange(desc(gamma)) %>%
  top_n(10) %>%
  htmlTable::htmlTable(align="l")
```

@@

```{r, message=FALSE, warning=FALSE, include=FALSE}
df <- btw.2 %>%
  filter(gamma >= 0.75) %>%
  distinct(title, .keep_all = T) %>%
  filter(topic %in% keep) %>%
  # Filter documents about the death of H.Geißler
  filter(!grepl("Geißler", title)) %>%
  # Filter outliner article (wrong topic assignment)
  filter(document != 9725) %>%
  filter(!grepl("Thermilindner", title, ignore.case = T))

@@

@@

btw.2 %>% 
  mutate(yearmonth = calculate_month(month(date),year(date))) %>%
  group_by(yearmonth, site) %>%
  summarise(total_obs = n()) -> tally_month_site
```

@@

polls <- table_long %>%
  mutate(month=month(Datum),
         year = year(Datum),
         yearmonth = calculate_month(month,year)) %>%
  group_by(yearmonth,party) %>%
  summarise(mean_val = mean(value, na.rm=T)) %>%
  ungroup() %>%
  filter(mean_val != "NaN") %>%
  select(party, yearmonth, mean_val) %>%
  spread(party, mean_val)
```

```{r fig.height=12, fig.width=10}
polls.red <- polls %>%
  filter(yearmonth > as.Date("2017-05-01")) %>%
  transmute(Union = normalize_data(Union),
         SPD = normalize_data(SPD),
         Grüne = normalize_data(Grüne),
         FDP = normalize_data(FDP),
         AfD = normalize_data(AfD),
         yearmonth = yearmonth)

# topics.red <- sentDF.values %>%
#   filter(grepl(paste("CDU","CSU","coalition", sep="|"), 
#                topic_name, ignore.case = T))
### by time
group1 <- sentDF.values %>%
  group_by(yearmonth, topic_name, topic) %>%
  summarise(sentiment = mean(sentiment, na.rm=T),
            obs = n()) %>%
  ungroup() %>%
  left_join(., tally_month, by="yearmonth") %>%
  mutate(w = obs / total_obs,
         sentiment_w = sentiment * w,
         sentiment_n = normalize_data(sentiment_w))

@@

```{r fig.height=5, fig.width=10}
ggplot(group1, aes(yearmonth, 
                   sentiment_n, 
                   group = topic_name,
                   color = topic_name)) +
  geom_line(show.legend = F) +
  facet_wrap(~topic_name, nrow = 3) +
  labs(x="", y="", title="Sentiment Score")
```

```{r}
polls.red %>%
  gather(key = party, value = poll, Union:AfD) %>%
  ggplot(aes(yearmonth, poll, color = party)) +
  geom_line() +
  labs(x="", y="", title = "Survey Value", color = "")
```

#### 3.1. Cross-Correlation
```{r}
group1 %>%
  select(yearmonth, topic_name, sentiment_n) %>%
  spread(topic_name, sentiment_n) %>%
  select(- yearmonth) -> corr1

polls.red %>% select(- yearmonth) -> corr2

@@

p1 <- ggplot() +
  geom_col(data=plot1, aes(yearmonth, sentiment_n, 
             group = topic_name,
             fill = topic_name),
           position = "dodge", 
           alpha = 0.8) +
  scale_fill_manual(values = col) +
    geom_line(data=plot1, aes(yearmonth, sentiment_n, 
             group = topic_name,
             color = topic_name),
             show.legend = F) +
  scale_color_manual(values = col) +
  guides(fill = guide_legend(ncol=3)) +
  # Add poll line
  geom_line(data = polls.red, 
            aes(yearmonth, Union),
            color = "black",
            size = 1) +
  labs(y="", x="", fill="",
       title = "Sentiment & Poll Values",
       subtitle = "Both scores are normalized") +
  scale_x_date(breaks = date_breaks("1 month"), labels=date_format("%B", tz="CET")) +
  theme(legend.position = "bottom")

@@

p2 <- ggplot() +
  geom_col(data = plot2,
           aes(yearmonth, sentiment_n, 
             group = topic_name,
             fill = topic_name),
           alpha = 0.8,
           position = "dodge") +
    scale_fill_manual(values = col) +
    scale_color_manual(values = col) +
  geom_line(data = plot2,
            aes(yearmonth, sentiment_n,
                group = topic_name,
                color = topic_name),
            show.legend = F) +
  facet_wrap(~site, ncol = 2) +
   # Add poll line
  geom_line(data = polls.red, 
            aes(yearmonth, Union),
            color = "black",
            size = 1) +
  labs(y="", x="", fill="") +
  scale_x_date(breaks = date_breaks("1 month"), labels=date_format("%B", tz="CET")) +
  theme(legend.position = "none",
        axis.text.x = element_text(angle = 90))

@@

### Plot 1  
p1 <- ggplot() +
  geom_col(data=plot1, aes(yearmonth, sentiment_n, 
             group = topic_name,
             fill = topic_name),
           position = "dodge", 
           alpha = 0.8) +
  scale_fill_manual(values = col) +
  guides(fill = guide_legend(ncol=3)) +
   geom_line(data=plot1, aes(yearmonth, sentiment_n, 
             group = topic_name,
             color = topic_name),
             show.legend = F) +
  scale_color_manual(values = col) +
  # Add poll line
  geom_line(data = polls.red, 
            aes(yearmonth, SPD),
            color = "red",
            size = 1) +
  labs(y="", x="", fill="",
       title = "Sentiment & Poll Values",
       subtitle = "Both scores are normalized") +
  scale_x_date(breaks = date_breaks("1 month"), labels=date_format("%B", tz="CET")) +
  theme(legend.position = "bottom")

@@

### Plot 2
p2 <- ggplot() +
  geom_col(data = plot2,
           aes(yearmonth, sentiment_n, 
             group = topic_name,
             fill = topic_name),
           alpha = 0.8,
           position = "dodge") +
  scale_fill_manual(values = col) +
  facet_wrap(~site, ncol = 2) +
     geom_line(data=plot2, aes(yearmonth, sentiment_n, 
             group = topic_name,
             color = topic_name),
             show.legend = F) +
  scale_color_manual(values = col) +
   # Add poll line
  geom_line(data = polls.red, 
            aes(yearmonth, SPD),
            color = "red",
            size = 1) +
  labs(y="", x="", fill="") +
  scale_x_date(breaks = date_breaks("1 month"), labels=date_format("%B", tz="CET")) +
  theme(legend.position = "none",
        axis.text.x = element_text(angle = 90))

>>>>

```{r}
topics <- matrix(c(1, "SPD, mainly M.Schulz", 2, "B90/ Die Grüne & DIE LINKE", 3, "Mix: Akhanli, Guttenberg, Bayern", 4, "Great Coalition debates", 5, "Diesel scandal", 6, "H.Kohl", 7, "Federal Election results", 8, "Europa, Macron, Schäuble", 9, "Mix: political trends, twitter", 10, "M.Schulz, mainly vs. A.Merkel", 11, "politics & democracy in GER", 12, "Deportation of criminal Refugees", 13, "A.Merkel, mainly election campaign", 14, "Text processing fail", 15, "Israel, antisemitism, D.Trump", 16, "Mix: political talkshows, Refugees", 17, "Debates within SPD", 18, "Election in Niedersachsen", 19, "N.Lammert", 20, "AfD, mainly right-wing radicalism", 21, "German armed forces, v.d.Leyen", 22, "SPD, mainly stuffing debates", 23, "CSU, mainly Söder & Seehover", 24, "Bundespräsident F.-W.Steinmeier", 25, "Election polls", 26, "Jamaica fail, Reelections or GroKo?", 27, "Jamaica Coalition debates", 28, "G20 in Hamburg", 29, "Federal Constitutional Court, Ministry of the Interior", 30, "AfD, mainly F.Petry & Meuthen", 31, "D.Trump, Russia", 32, "AfD, mainly Gauland & Weidel", 33, "German armed forces, Mali", 34, "Mix: Children, Education, Women", 35, "Left- rightwing Terror, police reports", 36, "Mix: people, Germany, democracy", 37, "AfD & DIE LINKE in parliament", 38, "EU policies", 39, "Mix: Terror attacks", 40, "Mix: Metoo, SPD", 41, "Terror attack Berlin (Amri)", 42, "Refugee family reunion", 43, "Mix: studies", 44, "Federal Constitutional Court (NSU, Franco, Terror)", 45, "Mix: minister of the interior, environment", 46, "CDU", 47, "Church", 48, "public (budget) statistics, Education/ Healthcare/ Digital policies", 49, "Turkey", 50, "Höcke, Holocaust"), ncol=2, byrow=T)

@@

```{r eval=FALSE, include=FALSE}
# Inspect some topics
btw.2 %>% filter(topic==37) %>% 
  select(title, gamma, site) %>%
  arrange(desc(gamma)) %>%
  htmlTable::htmlTable(align="l")
```

@@

```{r, message=FALSE, warning=FALSE, include=FALSE}
df <- btw.2 %>%
  filter(gamma >= 0.3) %>%
  distinct(title, .keep_all = T) %>%
  filter(topic %in% keep) %>%
  # Filter documents about the death of H.Geißler
  filter(!grepl("Geißler", title)) %>%
  # Filter outliner article (wrong topic assignment)
  filter(document != 9725) %>%
  filter(!grepl("Thermilindner", title, ignore.case = T))

@@

btw.2 %>% 
  mutate(yearweek = calculate_week(week(date), year(date))) %>%
  group_by(yearweek) %>%
  summarise(total_obs = n()) -> tally_week

@@

btw.2 %>% 
  mutate(yearmonth = calculate_month(month(date),year(date))) %>%
  group_by(yearmonth, site) %>%
  summarise(total_obs = n()) -> tally_month_site

btw.2 %>% 
  mutate(yearweek = calculate_week(week(date), year(date))) %>%
  group_by(yearweek, site) %>%
  summarise(total_obs = n()) -> tally_week_site
```

@@

polls <- table_long %>%
  mutate(yearmonth = calculate_month(month(Datum),year(Datum)),
         yearweek = calculate_week(week(Datum), year(Datum)))

## Monthly
polls_monthly <- polls %>%
  group_by(yearmonth,party) %>%
  summarise(mean_val = mean(value, na.rm=T)) %>%
  ungroup() %>%
  filter(mean_val != "NaN") %>%
  select(party, yearmonth, mean_val) %>%
  spread(party, mean_val) %>%
  filter(yearmonth > as.Date("2017-05-01")) %>%
  transmute(Union = normalize_data(Union),
         SPD = normalize_data(SPD),
         Grüne = normalize_data(Grüne),
         FDP = normalize_data(FDP),
         AfD = normalize_data(AfD),
         yearmonth = yearmonth)

polls_monthly %>%
  gather(key = party, value = poll, Union:AfD) %>%
  ggplot(aes(yearmonth, poll, color = party)) +
  geom_line() +
  scale_color_manual(values = c("skyblue", "gold", "limegreen", "red", "black")) +
  labs(x="", y="", title = "Survey Value", 
       subtitle = "weekly", color = "") +
  geom_vline(xintercept = as.Date("2017-09-24"), 
             linetype = 2, color = col[3]) +
  scale_x_date(breaks = date_breaks("1 month"), labels=date_format("%B", tz="CET"))
```

```{r fig.height=12, fig.width=10}
### by time
group1 <- sentDF.values %>%
  group_by(yearmonth, topic_name, topic) %>%
  summarise(sentiment = mean(sentiment, na.rm=T),
            obs = n()) %>%
  ungroup() %>%
  left_join(., tally_month, by="yearmonth") %>%
  mutate(w = obs / total_obs,
         sentiment_w = sentiment * w,
         sentiment_n = normalize_data(sentiment_w))

@@

#### 3.1. Cross-Correlation
```{r}
group1 %>%
  select(yearmonth, topic_name, sentiment_n) %>%
  spread(topic_name, sentiment_n)  -> corr1

polls_monthly %>% select(- yearmonth) -> corr2

@@

p1 <- ggplot() +
  geom_col(data=plot1, aes(yearmonth, sentiment_n, 
             group = topic_name,
             fill = topic_name),
           position = "dodge", 
           alpha = 0.8) +
  scale_fill_manual(values = col) +
    geom_line(data=plot1, aes(yearmonth, sentiment_n, 
             group = topic_name,
             color = topic_name),
             show.legend = F) +
  scale_color_manual(values = col) +
  guides(fill = guide_legend(ncol=3)) +
  # Add poll line
  geom_line(data = polls_monthly, 
            aes(yearmonth, Union),
            color = "black",
            size = 1) +
  labs(y="", x="", fill="",
       title = "Sentiment & Poll Values",
       subtitle = "Both scores are normalized") +
  scale_x_date(breaks = date_breaks("1 month"), labels=date_format("%B", tz="CET")) +
  theme(legend.position = "bottom")

@@

p2 <- ggplot() +
  geom_col(data = plot2,
           aes(yearmonth, sentiment_n, 
             group = topic_name,
             fill = topic_name),
           alpha = 0.8,
           position = "dodge") +
    scale_fill_manual(values = col) +
    scale_color_manual(values = col) +
  geom_line(data = plot2,
            aes(yearmonth, sentiment_n,
                group = topic_name,
                color = topic_name),
            show.legend = F) +
  facet_wrap(~site, ncol = 2) +
   # Add poll line
  geom_line(data = polls_monthly, 
            aes(yearmonth, Union),
            color = "black",
            size = 1) +
  labs(y="", x="", fill="") +
  scale_x_date(breaks = date_breaks("1 month"), labels=date_format("%B", tz="CET")) +
  theme(legend.position = "none",
        axis.text.x = element_text(angle = 90))

@@

### Plot 1  
p1 <- ggplot() +
  geom_col(data=plot1, aes(yearmonth, sentiment_n, 
             group = topic_name,
             fill = topic_name),
           position = "dodge", 
           alpha = 0.8) +
  scale_fill_manual(values = col) +
  guides(fill = guide_legend(ncol=3)) +
   geom_line(data=plot1, aes(yearmonth, sentiment_n, 
             group = topic_name,
             color = topic_name),
             show.legend = F) +
  scale_color_manual(values = col) +
  # Add poll line
  geom_line(data = polls_monthly, 
            aes(yearmonth, SPD),
            color = "red",
            size = 1) +
  labs(y="", x="", fill="",
       title = "Sentiment & Poll Values",
       subtitle = "Both scores are normalized") +
  scale_x_date(breaks = date_breaks("1 month"), labels=date_format("%B", tz="CET")) +
  theme(legend.position = "bottom")

@@

### Plot 2
p2 <- ggplot() +
  geom_col(data = plot2,
           aes(yearmonth, sentiment_n, 
             group = topic_name,
             fill = topic_name),
           alpha = 0.8,
           position = "dodge") +
  scale_fill_manual(values = col) +
  facet_wrap(~site, ncol = 2) +
     geom_line(data=plot2, aes(yearmonth, sentiment_n, 
             group = topic_name,
             color = topic_name),
             show.legend = F) +
  scale_color_manual(values = col) +
   # Add poll line
  geom_line(data = polls_monthly, 
            aes(yearmonth, SPD),
            color = "red",
            size = 1) +
  labs(y="", x="", fill="") +
  scale_x_date(breaks = date_breaks("1 month"), labels=date_format("%B", tz="CET")) +
  theme(legend.position = "none",
        axis.text.x = element_text(angle = 90))
